SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars

### 2015-09-06 papers/B1555_EdgeOn/B1555_letter.tex
Added two-contour figure and small tweak to text

The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}. This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}. The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear. While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.

@@

\begin{figure}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations of \citet{Marlow99} and the VLBA observations presented here overlaid.}
\label{fig:merlin}
\end{figure}

>>>>

The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}. This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}. The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear.  While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu14}.

%While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.

@@

\begin{figure}
%\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{fig2_twocontour_g.eps}
\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here overlaid.}
\label{fig:merlin}
\end{figure}
